---
title: "Test statistical assignment"
author: "Simone Long"
date: "27 January 2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading data (40 points)


```{r message=FALSE, warning=FALSE}

suppressMessages(library(tidyverse))

youth <- read_tsv("C:/Users/simon/OneDrive/Documents/datan3_2019/data/UKDA-6614-tab/tab/ukhls_w9/i_youth.tab")

```

## Tabulate variables (10 points)

```{r tables-youth}
dvagetab <- table(youth$i_dvage)
knitr::kable(dvagetab,
             col.names = c("Age", "Freq"),
             caption = "*Age Frequency*")

socwebtab <- table(youth$i_ypsocweb)
knitr::kable(socwebtab,
             col.names = c("On Social Media?", "Freq"),
             caption = "*Social Media Frequency*")

ypsextab <- table(youth$i_ypsex)
knitr::kable(ypsextab,
             col.names = c("Sex", "Freq"),
             caption = "*Sex Frequency*")
```

## Recode variables (10 points)

```{r}

youth$i_ypsocweb_bin <- NA
youth$i_ypsocweb_bin[youth$i_ypsocweb == 1] <- 1
youth$i_ypsocweb_bin[youth$i_ypsocweb == 2] <- 0
youth$i_ypsocweb_bin[youth$i_ypsocweb == -9] <- NA

youth$i_sex_bin <- ifelse(youth$i_ypsex == 1, "Male", "Female")

```

## Calculate means (10 points)

```{r}

prob.age_socweb <- tapply(youth$i_ypsocweb_bin, youth$i_age_dv, mean, na.rm = TRUE)
knitr::kable(prob.age_socweb,
             col.names = c("Probability of Having Social Media"),
             caption = "*Probability of Being on Social Media Relative to Age*")

prob.sex_socweb <- tapply(youth$i_ypsocweb_bin, youth$i_sex_bin, mean, na.rm = TRUE)
knitr::kable(prob.sex_socweb,
             col.names = c("Probability of Having Social Media"),
             caption = "*Probability of Being on Social Media Relative to Sex*")

```

## Write short interpretation (10 points)

There appears to be a generally positive trend in the probability of being on social media relative to age; the older a young person is, the more likely they are to have an online presence. As far as gender/sex is concerned, women seem to have a higher probability of having social media (specificially, a 6% greater likelihood). It stands to reason, therefore, that 16 year-old girls are most likely to be active on social media.

## Visualise results (20 points)

```{r warning=FALSE}
library(ggplot2)

ggplot(youth, aes(x = factor(i_age_dv))) +
  stat_summary_bin(aes(y = i_ypsocweb_bin), fun.y = "mean", geom = "bar", binwidth = 0.5) +
  theme(axis.text.x = element_text(size = 9, angle = 45)) + facet_grid(. ~ i_sex_bin)
  
```